---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# psifrr

<!-- badges: start -->
<!-- badges: end -->

Analysis and visualization of free recall data.

PsifrR currently relies on the Psifr Python package, which is called from R using the `reticulate` package.

## Installation

First, install `devtools` and `reticulate`:

``` r
install.packages("reticulate")
install.packages("devtools")
```

Follow the `reticulate` package [documentation](https://rstudio.github.io/reticulate/index.html) to set up a Python environment.

Next, install the Psifr Python package:

``` r
py_install("git+https://github.com/mortonne/psifr.git@reticulate", pip=TRUE)
```

Finally, install psifrr from [GitHub](https://github.com/) with:

``` r
devtools::install_github("mortonne/psifrr")
```

## Working with free recall data

To load a sample dataset in [Psifr format](https://psifr.readthedocs.io/en/stable/guide/import.html):

```{r}
library(psifrr)
raw <- sample_data("Morton2013")
head(raw)
```

To analyze a dataset, we need to first score it by matching up study items to recalled items.
See [Scoring data](https://psifr.readthedocs.io/en/stable/guide/score.html) for details.

```{r}
data <- merge_free_recall(raw)
```

We can use `filter_data` to a select one list for a sample of what the results look like:

```{r}
filter_data(data, subjects = 1, lists = 1)
```

See [Managing data](https://psifr.readthedocs.io/en/latest/api/fr.html#managing-data)
for a full list of functions that operate on free recall data.
