---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# psifrr

<!-- badges: start -->
<!-- badges: end -->

Analysis and visualization of free recall data.

PsifrR is currently relies on the Psifr Python package. It calls Psifr using the `reticulate` package.

## Installation

First, install `devtools` and `reticulate`:

``` r
install.packages("reticulate")
install.packages("devtools")
```

Follow the `reticulate` package [documentation](https://rstudio.github.io/reticulate/index.html) to set up a Python environment.

Next, install the Psifr Python package:

``` r
py_install("git+https://github.com/mortonne/psifr.git@reticulate", pip=TRUE)
```

Finally, install psifrr from [GitHub](https://github.com/) with:

``` r
devtools::install_github("mortonne/psifrr")
```

## Example

To load a sample dataset:

```{r example}
library(psifrr)
raw <- sample_data("Morton2013")
```
